[dcpo_demsupport] Appendix

### 2020-07-04 paper/dcpo_demsupport_appendix.Rmd
save claassen_replication_input.rda

claassen_input <- DCPOtools::format_claassen(claassen_input_raw1)
save(claassen_input, file = here::here("data", "claassen_input.rda"))

>>>>

claassen_replication_input <- DCPOtools::format_claassen(claassen_input_raw1)
save(claassen_replication_input, file = here::here("data", "claassen_replication_input.rda"))
